\Large \includegraphics[height=\baselineskip]{title} \\ \vspace{0.025 in} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-06 docs/paper.tex
Paper outline

\section{Introduction}
TODO

\section{Section}
TODO

\section{Availability}
TODO~\cite{ipv4sta}\endnote{Endnote}

>>>>

\section{Introduction}
TODO
- Introduction to the problem
- Enumeration of sections this paper talks about

\section{Background}
TODO
- DNS: explanation
- IDN: history, explanation
- Browsers: display of IDNs, algorithms

\section{Related Work}
TODO
- Brief analysis of previous papers on the same topic

\section{Methodology}
TODO
- Introduction to the methodology
- Subsection: data collection
- Subsection: data pre-processing
- Subsection: clustering, confusables algorithm
- Subsection: manual classification, guidelines used

\section{Results}
TODO
- Different results obtained

\section{Ethical Considerations}
TODO
- Brief explanation why this research is ethical

\section{Conclusions}
TODO
- Conclusions of our work
- Possible future work

\section*{Acknowledgements}
- Thank prof/TA
TODO~\cite{ipv4sta}\endnote{Endnote}
